Progress with the NOSAMS<br>Hybrid Gas Ion Source

### 2021-05-02 doc/SNEAP2021/SNEAP2021_HGIS_presentation/SNEAP2021_HGIS_presentation.Rmd
Tweak figure legend

secs <- ggplot(carb_data, aes(fm_consensus, fm_diff, color = Cur)) +
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_pointrange(aes(ymin = fm_diff - merr, ymax = fm_diff + merr), 
                  position = position_dodge2(width = dw),
                  size = ps,) +
  lims(x = c(-0.05, 1.1),
       y = c(-yl, yl)) +
  labs(title = "Difference from expected Fm",
       subtitle = "Uncorrected",
       colour = "Cur (μA)",
       y = "Fm difference") +
  theme_classic() +
  theme_xaringan(title_font_size = 18,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.direction = "horizontal",
        legend.position = c(.84, 1),
        legend.justification = "bottom")

>>>>

secs <- ggplot(carb_data, aes(fm_consensus, fm_diff, color = Cur)) +
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_pointrange(aes(ymin = fm_diff - merr, ymax = fm_diff + merr), 
                  position = position_dodge2(width = dw),
                  size = ps,) +
  lims(x = c(-0.05, 1.1),
       y = c(-yl, yl)) +
  labs(title = "Difference from expected Fm",
       subtitle = "Uncorrected",
       colour = "Cur (μA)",
       y = "Fm difference") +
  theme_classic() +
  theme_xaringan(title_font_size = 18,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.direction = "horizontal",
        legend.position = c(.80, 1),
        legend.justification = "bottom")
